### 2022-09-17 main/chapter_2ljets.tex
add note and ref for claimed good coverage
add cr vr sr figure; improve histfitter citation; add some notes

Worse, I disregarded the popular idea that every region should have a large
background expectation, preferably of ten events or more.
This requirement is typically justified by the limitations of approximate
statistical methods that work
``from as few as $\mathcal{O}(10)$ data events''~\cite{histfitter2014}.
But the Poisson likelihood works for infinitesimally small
expectations~\cite{skilling2009cosmology}, and in the small-bin limit one has
continuous of `unbinned' distributions with Poisson normalizations
(sometimes called ``extended'' in High-Energy
Physics~\cite{barlow1990extended})
that are standard elsewhere in High-Energy Physics,
and are easily analysed by the standard likelihood fitting
methods~\cite{cowan1998statistical}.
Examples uses of unbinned modelling include analyses of hadronic
resonances in
\lhcb~\cite{Tullythesis,lhcb2018563}, searches for exotic effects in
\atlas~\cite{EXOT-2018-08},
and notably the observation of the
Higgs boson~\cite{HIGG-2012-27}.

@@

In an apparent notional effort to address this problem, we treat the signal
cross-section specially by not fitting it within a constraint, but fixing it
to central, up, and down values for three repeated analyses.
We then derive and report separate exclusion contours for each cross-section
variation;
such alternative contours are shown as the three observed limits
in Figures~\ref{fig:2ljets_contours_c1n2} and~\ref{fig:2ljets_contours_gmsb}.
This approach is entirely standard, and is indeed ingrained into \histfitter\
through the special parameter name
\texttt{SigXSec}~\cite{histfitter2014, histfittergithub}.

>>>>

Worse, I disregarded the popular idea that every region should have a large
background expectation, preferably of ten events or more.
This requirement is typically justified by the limitations of approximate
statistical methods which work
``from as few as $\mathcal{O}(10)$ data events''~\cite{histfitter2015}.
But the Poisson likelihood works for infinitesimally small
expectations~\cite{skilling2009cosmology}, and in the small-bin limit one has
continuous of `unbinned' distributions with Poisson normalizations
(sometimes called ``extended'' in High-Energy
Physics~\cite{barlow1990extended})
that are standard elsewhere in High-Energy Physics,
and are easily analysed by the standard likelihood fitting
methods~\cite{cowan1998statistical}.
Examples uses of unbinned modelling include analyses of hadronic
resonances in
\lhcb~\cite{Tullythesis,lhcb2018563}, searches for exotic effects in
\atlas~\cite{EXOT-2018-08},
and notably the observation of the
Higgs boson~\cite{HIGG-2012-27}.

@@

In an apparent notional effort to address this problem, we treat the signal
cross-section specially by not fitting it within a constraint, but fixing it
to central, up, and down values for three repeated analyses.
We then derive and report separate exclusion contours for each cross-section
variation;
such alternative contours are shown as the three observed limits
in Figures~\ref{fig:2ljets_contours_c1n2} and~\ref{fig:2ljets_contours_gmsb}.
This approach is entirely standard, and is indeed ingrained into \histfitter\
through the special parameter name
\texttt{SigXSec}~\cite{histfitter2015, histfittergithub}.

### 2022-09-17 main/chapter_searches.tex
add cr vr sr figure; improve histfitter citation; add some notes

Our searches see data only through discrete histogram bins,
or `regions', which are defined by logical selections in event variables.
To communicate their intended uses, we further categorize these bins into
`control', `validation', and `signal' regions.

@@

\paragraph{Validation regions (VRs).}
To represent the Standard Model, control regions must be insensitive to
non-standard signals.
Before applying their normalization factors to regions that are sensitive
to signal hypotheses, data in \textbf{validation regions} (\textbf{VR}s) first
test the quality of extrapolation.
Each model is adjusted until validation region data are well predicted ---
either by changing region definitions or restructuring the \heplikelihood\
model, perhaps with extrapolation uncertainties or extra normalization
factors.
Likelihoods for validation region data are not included in the \heplikelihood\
models, but their data are important and indirectly used to update the
model in this manner.

\paragraph{Signal regions (SRs).}
Consuming information from control and validation regions to refine the
predictions of our background-only model is scientific learning, and can be
reconciled with machine learning practice as fitting a model with training
(CR) and validation (VR) data.
Testing is performed through in prediction of data in the
\textbf{signal regions} (\textbf{SR}s),
in which signal yields should significantly add on top of the Standard Model
backgrounds.
Some signal regions are also labelled \textbf{DR} to indicate their use in
specific `discovery' fits.

\TODO{Figure to illustrate CR VR SR extrapolation}

\paragraph{Fits.}
\TODO{Background-only}

\TODO{Exclusion (model-dependent signal}

\TODO{Discovery (model-independent signal)}

@@

>>>>

Our searches see data only through discrete histogram bins,
or `regions', which are defined by logical selections in event variables.
To communicate their intended uses, we further categorize these bins into
`control', `validation', and `signal' regions;
Figure~\ref{fig:searches_histfitter_regions} illustrates the uses of these
three region types.

\begin{figure}[tp]
\centering
\includegraphics[width=0.6\textwidth]{figures/searches_histfitter_regions.pdf}
\caption[
Control, validation, and signal regions
]{%
Control, validation, and signal regions and the extrapolation between them.
Both observables are event variables in which models should change
smoothly to justify the extrapolations that are indicated by arrows.
Dashed lines illustrate the each region may be subclassified into
disjoint (orthogonal) smaller bins.
Adapted from \histfitter~\cite{histfitter2015}.
}
\label{fig:searches_histfitter_regions}
\end{figure}

@@

\paragraph{Validation regions (VRs).}
To represent the Standard Model, control regions must be insensitive to
non-standard signals.
Before applying their normalization factors to regions that are sensitive
to signal hypotheses, data in validation regions first
test the quality of extrapolation.
Each model is adjusted until validation region data are well predicted ---
either by changing region definitions or restructuring the \heplikelihood\
model, perhaps with extrapolation uncertainties or extra normalization
factors.
Likelihoods for validation region data are not included in the \heplikelihood\
models, but their data are important and indirectly used to update the
model in this manner.

\paragraph{Signal regions (SRs).}
Consuming information from control and validation regions to refine the
predictions of our background-only model is scientific learning, and can be
reconciled with machine learning practice as fitting a model with training
(CR) and validation (VR) data.
Testing is done by predicting of data in the signal regions,
in which signal yields should significantly add on top of the Standard Model
backgrounds.
Some signal regions are labelled as \textbf{discovery regions} (\textbf{DRs})
to indicate their use in special `discovery' fits.

\paragraph{Background-only fits.}
\TODO{Background-only}
% summary plots
% fit to just CR, show VR and SR
% conventional to also show SR
% this is more like a posterior
% so not easily interpreted

\paragraph{Exclusion fits.}
\TODO{Exclusion (model-dependent signal}
% CLs

\paragraph{Discovery fits.}
\TODO{Discovery (model-independent signal)}
% CLs and p-value
% maximum likelihood ratio test statistics
% despite likeliy superiority of $n$

@@

% tail area

% maximum likelihood ratio

% similarity and difference
